### 2019-02-27 appendices/proofs.tex
use cleveref consistently

\subsection{Theorem~\ref{thm:pres-eval}}

\begin{proof}
  We prove Theorem~\ref{thm:pres-eval} by induction on $e$:

@@

\subsection{Lemma~\ref{lem:presvalue}}

\begin{proof}
  We prove Lemma~\ref{lem:presvalue} by induction over $e$.

@@

\subsection{Theorem~\ref{thm:pres-stride}}

\begin{proof}
  We prove Theorem~\ref{thm:pres-stride} by induction on $e$:

@@

  \case{$\userule{S-ThenCont}$}
  {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$, by \refrule{T-Then} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction hypothesis, we
  know that $t_1\stride t_1'$ preserves. By Lemma~\ref{lem:presvalue}, we know
  that $\Value{(t_1')}=v_1$ preserves. By Theorem~\ref{thm:pres-eval} we know
  that $e_2 v_1\evaluate t_2$ preserves. And finally by the induction hypothesis,
  we know that $t_2\stride t_2'$ preserves. Therefore
  $\Gamma,\Sigma\infers t_2':\Task\tau$.}
  %
  % \noindent\textbf{Case} $\userule{S-Appoint}$ Given that
  % $\Gamma,\Sigma\infers u\At t:\Task\tau$, by \refrule{T-Appoint} we have
  % $t:\Task\tau$. By the induction hypothesis, we know that $t,s\stride t',s'$
  % preserves, and thus $\Gamma,\Sigma\infers u\At t':\Task\tau$.

@@

\subsection{Theorem~\ref{thm:pres-norm}}

\begin{proof}
  We prove Theorem~\ref{thm:pres-norm} by induction on $e$:

  \case{$\userule{N-Done}$}
    {Given that
    $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that
    $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
    Theorem~\ref{thm:pres-eval}. Then by Theorem~\ref{thm:pres-stride}, we have
    $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$.}

  \case
    {$\userule{N-Repeat}$}
    { Given that
    $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that
    $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
    Theorem~\ref{thm:pres-eval}. Then by Theorem~\ref{thm:pres-stride}, we have
    $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$. Then by the
    induction hypothesis, we finally obtain that
    $\Gamma,\Sigma\infers t'':\Task\tau$ and $\Sigma\infers s'''$.}

@@

\subsection{Theorem~\ref{thm:pres-handle}}

@@

\begin{proof}
  We prove Theorem~\ref{thm:pres-handle} by induction on $e$:

@@

  \case
    {$\userule{H-Update}$}
    {Given that $\Gamma,\Sigma\infers\Update l:\Task\tau$ and $\Sigma\infers s$.
    This gives us that $\Sigma(l)=\tau$, and we additionally obtain $s(l),v':\tau$ by \refrule{H-Update}.
    By application of Lemma~\ref{lemmasigmaconsistent} this case holds.}

@@

% \subsection{Theorem~\ref{thmprogressnorm}}
%
% \begin{proof} We prove this Theorem by induction on $e$.\\
%
%   \noindent\textbf{Case} $\userule{S-Edit}$ Given that $\Gamma,\Sigma\infers \Edit v : \Task \tau$, let $e''=\Edit v'$, $s''=s$ and $i=v':\tau$. Then H-Edit gives $\Edit v,s\handle{v'}\Edit v',s$. \\
%
%
%   \noindent\textbf{Case} $\userule{S-Fill}$ Given that $\Gamma,\Sigma\infers \Enter \tau : \Task \tau$, let $e''=\Edit v$, $s''=s$ and $i=v:\tau$. Then H-Fill gives $\Enter \tau,s\handle{v}\Edit v,s$. \\
%
%   \noindent\textbf{Case} $\userule{S-Update}$ Given that $\Gamma,\Sigma\infers \Update l : \Task \tau$, let $e''=\Update l$, $s''=s[l\mapsto v]$ and $i=v:\tau$. Then H-Update gives $\Update l ,s\handle{v}\Update l,s[l\mapsto v]$. \\
%
%   \noindent\textbf{Case} $\userule{S-Fail}$ Since $\Failing(\Fail)=\True$, the theorem holds in this case. \\
%
%   \noindent\textbf{Case} $\userule{S-Xor}$ \todo{Here we have an issue with the defintion of $\Failing$ and the sideconditions of external choice. These definitions should concur, so we can finish the proof, but $\Failing$ is a static property}\\
%
%   \noindent\textbf{Case} $\userule{S-Eval}$ By induction hypothesis we have that there exists an $e'''$, $s'''$ and $i$ such that $e'',s''\handle{i}e''',s'''$.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenStay}$ By the induction hyposthesis we have that there exists an $e''$, $s''$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by H-Pass, we know that we can apply the same $i$ to obtain $t_1\Then e_2,s'\handle{i} e''\Then e,s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenFail}$ By the induction hyposthesis we have that there exists an $e''$, $s''$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by H-Pass, we know that we can apply the same $i$ to obtain $t_1\Then e_2,s'\handle{i} e''\Then e,s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenCont}$ By the induction hypothesis, we have that there exists an $e''$, $s''''$ and $i$ such that $t_2',s''\handle{i}e'',s''''$.\\
%
%   \noindent\textbf{Case} $\userule{S-OrLeft}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_1',s\handle{i}e'',s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-OrRight}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_2',s\handle{i}e'',s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-OrNone}$ \todo{   }\\
%
%   \noindent\textbf{Case} $\userule{S-Next}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by the H-PassNext rule, we know that we can apply the same $i$ to obtain $t_1'\Next e_2,s'\handle{i}e'',s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-And}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by the H-FirstOr rule, we know that we can apply $\First i$ to obtain $t_1'\And t_2',s'\handle{\First i} t_1''\And t_2',s''$
%
% \end{proof}

% \subsection{Lemma~\ref{lem:stride-does-not-eval}}
%
% \begin{proof}
%   We prove Lemma~\ref{lem:stride-does-not-eval} by induction on $e$. First we
%   apply evaluation, and we then find ourselves in one of the cases below.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenStay}$\\
%   and $\userule{S-ThenFail}$ The \refrule{E-Then} rule gives us that evaluation
%   has been applied to $t_1$. We therefore can apply the induction hypothesis,
%   from which we obtain that $t_1',s'\evaluate t_1'',s''$ then $t_1'=t_1''$ and
%   $s'=s''$. This, together with the \refrule{E-Then} rule, proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenCont}$ By application of the induction
%   hypothesis, we obtain that $t_2',s'''\evaluate t_2'',s''''$ then $t_2'=t_2''$
%   and $s'''=s''''$, which immediately proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-OrLeft}$ The \refrule{E-Or} rule gives us
%   that evaluation has been applied to $t_1$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t_1',s'\evaluate t_1'',s''$
%   then $t_1'=t_1''$ and $s'=s''$, which immediately proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-OrRight}$The \refrule{E-Or} rule gives us
%   that evaluation has been applied to $t_2$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t_2',s'\evaluate t_2'',s''$
%   then $t_2'=t_2''$ and $s'=s''$, which immediately proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-OrNone}$ The \refrule{E-Or} rule gives us
%   that evaluation has been applied to both $t_1$ and $t_1$. We assumed that the
%   states do not change, so we know that $s=s'=s''$. We can therefore safely
%   apply the induction hypothesis twice, to obtain that
%   $t_1',s''\evaluate t_1'',s'''$ then $t_1'=t_1''$ and $s''=s'''$, and
%   $t_2',s'''\evaluate t_2'',s''''$ then $t_2'=t_2''$ and $s'''=s''''$. This,
%   together with the \refrule{E-Or} rule proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-Edit}$ by definiton, $\Edit v$ is a value
%   with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Fill}$ by definition, $\Enter \tau$ is a
%   value with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Update}$ by definiton, $\Update l$ is a
%   value with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Fail}$ by definiton, $\Fail$ is a value
%   with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Xor}$ by definition, $e_1\Xor e_2$ is a
%   value with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Next}$ The \refrule{E-Next} rule gives us
%   that evaluation has been applied to $t_1$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t_1',s'\evaluate t_1'',s''$
%   then $t_1'=t_1''$ and $s'=s''$. This, together with the \refrule{E-Next} rule,
%   proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-And}$ The \refrule{E-And} rule gives us
%   that evaluation has been applied to both $t_1$ and $t_1$. We assumed that the
%   states do not change, so we know that $s=s'=s''$. We can therefore safely
%   apply the induction hypothesis twice, to obtain that
%   $t_1',s''\evaluate t_1'',s'''$ then $t_1'=t_1''$ and $s''=s'''$, and
%   $t_2',s'''\evaluate t_2'',s''''$ then $t_2'=t_2''$ and $s'''=s''''$. This,
%   together with the \refrule{E-And} rule proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-Appoint}$ The \refrule{E-Appoint} rule
%   gives us that evaluation has been applied to $t$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t',s'\evaluate t'',s''$ then
%   $t'=t''$ and $s'=s''$. This, together with the \refrule{E-Appoint} rule,
%   proves this case.
%
% \end{proof}

\subsection{Theorem~\ref{thm:failing}}

@@

  We prove Theorem~\ref{thm:failing} by induction on $e'$.

@@

\subsection{Theorem~\ref{thm:safety-i}}

>>>>

\subsection{\cref{thm:pres-eval}}

\begin{proof}
  We prove \cref{thm:pres-eval} by induction on $e$:

@@

\subsection{\cref{lem:presvalue}}

\begin{proof}
  We prove \cref{lem:presvalue} by induction over $e$.

@@

\subsection{\cref{thm:pres-stride}}

\begin{proof}
  We prove \cref{thm:pres-stride} by induction on $e$:

@@

  \case{$\userule{S-ThenCont}$}
  {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$, by \refrule{T-Then} we have
  $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and
  $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$. By the induction hypothesis, we
  know that $t_1\stride t_1'$ preserves. By \cref{lem:presvalue}, we know
  that $\Value{(t_1')}=v_1$ preserves. By \cref{thm:pres-eval} we know
  that $e_2 v_1\evaluate t_2$ preserves. And finally by the induction hypothesis,
  we know that $t_2\stride t_2'$ preserves. Therefore
  $\Gamma,\Sigma\infers t_2':\Task\tau$.}
  %
  % \noindent\textbf{Case} $\userule{S-Appoint}$ Given that
  % $\Gamma,\Sigma\infers u\At t:\Task\tau$, by \refrule{T-Appoint} we have
  % $t:\Task\tau$. By the induction hypothesis, we know that $t,s\stride t',s'$
  % preserves, and thus $\Gamma,\Sigma\infers u\At t':\Task\tau$.

@@

\subsection{\Cref{thm:pres-norm}}

\begin{proof}
  We prove \cref{thm:pres-norm} by induction on $e$:

  \case{$\userule{N-Done}$}
    {Given that
    $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
    \Cref{thm:pres-eval}.
    Then by \cref{thm:pres-stride}, we have $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$.}

  \case
    {$\userule{N-Repeat}$}
    { Given that $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by \cref{thm:pres-eval}.
    Then by \cref{thm:pres-stride}, we have $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$.
    Then by the induction hypothesis, we finally obtain that $\Gamma,\Sigma\infers t'':\Task\tau$ and $\Sigma\infers s'''$.}

@@

\subsection{\cref{thm:pres-handle}}

@@

\begin{proof}
  We prove \cref{thm:pres-handle} by induction on $e$:

@@

  \case
    {$\userule{H-Update}$}
    {Given that $\Gamma,\Sigma\infers\Update l:\Task\tau$ and $\Sigma\infers s$.
    This gives us that $\Sigma(l)=\tau$, and we additionally obtain $s(l),v':\tau$ by \refrule{H-Update}.
    By application of \cref{lemmasigmaconsistent} this case holds.}

@@

% \subsection{\cref{thmprogressnorm}}
%
% \begin{proof} We prove this Theorem by induction on $e$.\\
%
%   \noindent\textbf{Case} $\userule{S-Edit}$ Given that $\Gamma,\Sigma\infers \Edit v : \Task \tau$, let $e''=\Edit v'$, $s''=s$ and $i=v':\tau$. Then H-Edit gives $\Edit v,s\handle{v'}\Edit v',s$. \\
%
%
%   \noindent\textbf{Case} $\userule{S-Fill}$ Given that $\Gamma,\Sigma\infers \Enter \tau : \Task \tau$, let $e''=\Edit v$, $s''=s$ and $i=v:\tau$. Then H-Fill gives $\Enter \tau,s\handle{v}\Edit v,s$. \\
%
%   \noindent\textbf{Case} $\userule{S-Update}$ Given that $\Gamma,\Sigma\infers \Update l : \Task \tau$, let $e''=\Update l$, $s''=s[l\mapsto v]$ and $i=v:\tau$. Then H-Update gives $\Update l ,s\handle{v}\Update l,s[l\mapsto v]$. \\
%
%   \noindent\textbf{Case} $\userule{S-Fail}$ Since $\Failing(\Fail)=\True$, the theorem holds in this case. \\
%
%   \noindent\textbf{Case} $\userule{S-Xor}$ \todo{Here we have an issue with the defintion of $\Failing$ and the sideconditions of external choice. These definitions should concur, so we can finish the proof, but $\Failing$ is a static property}\\
%
%   \noindent\textbf{Case} $\userule{S-Eval}$ By induction hypothesis we have that there exists an $e'''$, $s'''$ and $i$ such that $e'',s''\handle{i}e''',s'''$.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenStay}$ By the induction hyposthesis we have that there exists an $e''$, $s''$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by H-Pass, we know that we can apply the same $i$ to obtain $t_1\Then e_2,s'\handle{i} e''\Then e,s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenFail}$ By the induction hyposthesis we have that there exists an $e''$, $s''$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by H-Pass, we know that we can apply the same $i$ to obtain $t_1\Then e_2,s'\handle{i} e''\Then e,s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenCont}$ By the induction hypothesis, we have that there exists an $e''$, $s''''$ and $i$ such that $t_2',s''\handle{i}e'',s''''$.\\
%
%   \noindent\textbf{Case} $\userule{S-OrLeft}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_1',s\handle{i}e'',s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-OrRight}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_2',s\handle{i}e'',s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-OrNone}$ \todo{   }\\
%
%   \noindent\textbf{Case} $\userule{S-Next}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by the H-PassNext rule, we know that we can apply the same $i$ to obtain $t_1'\Next e_2,s'\handle{i}e'',s''$.\\
%
%   \noindent\textbf{Case} $\userule{S-And}$ By the induction hypothesis, we have that there exists an $e''$, $s'$ and $i$ such that $t_1',s'\handle{i}e'',s''$. Then by the H-FirstOr rule, we know that we can apply $\First i$ to obtain $t_1'\And t_2',s'\handle{\First i} t_1''\And t_2',s''$
%
% \end{proof}

% \subsection{\cref{lem:stride-does-not-eval}}
%
% \begin{proof}
%   We prove \cref{lem:stride-does-not-eval} by induction on $e$. First we
%   apply evaluation, and we then find ourselves in one of the cases below.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenStay}$\\
%   and $\userule{S-ThenFail}$ The \refrule{E-Then} rule gives us that evaluation
%   has been applied to $t_1$. We therefore can apply the induction hypothesis,
%   from which we obtain that $t_1',s'\evaluate t_1'',s''$ then $t_1'=t_1''$ and
%   $s'=s''$. This, together with the \refrule{E-Then} rule, proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-ThenCont}$ By application of the induction
%   hypothesis, we obtain that $t_2',s'''\evaluate t_2'',s''''$ then $t_2'=t_2''$
%   and $s'''=s''''$, which immediately proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-OrLeft}$ The \refrule{E-Or} rule gives us
%   that evaluation has been applied to $t_1$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t_1',s'\evaluate t_1'',s''$
%   then $t_1'=t_1''$ and $s'=s''$, which immediately proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-OrRight}$The \refrule{E-Or} rule gives us
%   that evaluation has been applied to $t_2$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t_2',s'\evaluate t_2'',s''$
%   then $t_2'=t_2''$ and $s'=s''$, which immediately proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-OrNone}$ The \refrule{E-Or} rule gives us
%   that evaluation has been applied to both $t_1$ and $t_1$. We assumed that the
%   states do not change, so we know that $s=s'=s''$. We can therefore safely
%   apply the induction hypothesis twice, to obtain that
%   $t_1',s''\evaluate t_1'',s'''$ then $t_1'=t_1''$ and $s''=s'''$, and
%   $t_2',s'''\evaluate t_2'',s''''$ then $t_2'=t_2''$ and $s'''=s''''$. This,
%   together with the \refrule{E-Or} rule proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-Edit}$ by definiton, $\Edit v$ is a value
%   with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Fill}$ by definition, $\Enter \tau$ is a
%   value with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Update}$ by definiton, $\Update l$ is a
%   value with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Fail}$ by definiton, $\Fail$ is a value
%   with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Xor}$ by definition, $e_1\Xor e_2$ is a
%   value with respect to evaluation.\\
%
%   \noindent\textbf{Case} $\userule{S-Next}$ The \refrule{E-Next} rule gives us
%   that evaluation has been applied to $t_1$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t_1',s'\evaluate t_1'',s''$
%   then $t_1'=t_1''$ and $s'=s''$. This, together with the \refrule{E-Next} rule,
%   proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-And}$ The \refrule{E-And} rule gives us
%   that evaluation has been applied to both $t_1$ and $t_1$. We assumed that the
%   states do not change, so we know that $s=s'=s''$. We can therefore safely
%   apply the induction hypothesis twice, to obtain that
%   $t_1',s''\evaluate t_1'',s'''$ then $t_1'=t_1''$ and $s''=s'''$, and
%   $t_2',s'''\evaluate t_2'',s''''$ then $t_2'=t_2''$ and $s'''=s''''$. This,
%   together with the \refrule{E-And} rule proves this case.\\
%
%   \noindent\textbf{Case} $\userule{S-Appoint}$ The \refrule{E-Appoint} rule
%   gives us that evaluation has been applied to $t$. We therefore can apply the
%   induction hypothesis, from which we obtain that $t',s'\evaluate t'',s''$ then
%   $t'=t''$ and $s'=s''$. This, together with the \refrule{E-Appoint} rule,
%   proves this case.
%
% \end{proof}

\subsection{\cref{thm:failing}}

@@

  We prove \cref{thm:failing} by induction on $e'$.

@@

\subsection{\cref{thm:safety-i}}

### 2019-02-27 sections/introduction.tex
some fixmes
use cleveref consistently

Both implementations currently lack formal semantics which can be used to prove properties about tasks.\fixme{Rinus: can be used.. -> is suited}

@@

In Section~\ref{sec:example} we demonstrate the functionality of \TOPHAT by means of an example,
Section~\ref{sec:intuition} gives an overview of the essential concepts of \TOP and \TOPHAT.
Section~\ref{sec:language} introduces the \TOPHAT calculus syntax
and Section~\ref{sec:semantics} the semantics.
Then in Section~\ref{sec:properties} we show that certain properties hold for the calculus.
We take a look at related work in Section~\ref{sec:relatedwork}
and conclude in Section~\ref{sec:conclusions}.

>>>>

Both implementations currently lack formal semantics which are suited to prove properties about tasks.

@@

In \cref{sec:example} we demonstrate the functionality of \TOPHAT by means of an example,
\Cref{sec:intuition} gives an overview of the essential concepts of \TOP and \TOPHAT.
\Cref{sec:language} introduces the \TOPHAT calculus syntax
and \cref{sec:semantics} the semantics.
Then in \cref{sec:properties} we show that certain properties hold for the calculus.
We take a look at related work in \cref{sec:relatedwork}
and conclude in \cref{sec:conclusions}.

### 2019-02-27 sections/outlook.tex
use cleveref consistently

Firstly, we would like to express properties of tasks and prove them.
For example, one would like to prove that, no matter what, in Example~\ref{exm:breakfast} breakfast is always being served.
Secondly, we would like to explore what it means for two tasks to be equal.
One could have noticed that some operators have a monadic or applicative feeling.
The combination of $\And$ and $\Edit$ could form a (lax) monoidal functor,
$\Or$ is similar to applicative choice,
and $\Then$ looks like a bind operation.
We need a correct understand of equivalence of tasks,
taking the interactive setting into account,
to prove this.
Thirdly, we do not know yet if the more complex combinators of \ITASKS are expressible in the basic combinators of \TOPHAT.
We implemented \TOPHAT on top of \ITASKS, so we know it is a subset,
but we also know \ITASKS can do more.

@@

A more in depth description of future work can be found in Section~\ref{sec:conclusions}.

>>>>

Firstly, we would like to express properties of tasks and prove them.
For example, one would like to prove that, no matter what, in \cref{exm:breakfast} breakfast is always being served.
Secondly, we would like to explore what it means for two tasks to be equal.
One could have noticed that some operators have a monadic or applicative feeling.
The combination of $\And$ and $\Edit$ could form a (lax) monoidal functor,
$\Or$ is similar to applicative choice,
and $\Then$ looks like a bind operation.
We need a correct understand of equivalence of tasks,
taking the interactive setting into account,
to prove this.
Thirdly, we do not know yet if the more complex combinators of \ITASKS are expressible in the basic combinators of \TOPHAT.
We implemented \TOPHAT on top of \ITASKS, so we know it is a subset,
but we also know \ITASKS can do more.

@@

A more in depth description of future work can be found in \cref{sec:conclusions}.

### 2019-02-27 sections/properties.tex
use cleveref consistently

Theorem~\ref{thm:pres-eval} is shown to be correct by induction over $e$. The full
proof can be found in the appendix.

@@

Lemma~\ref{lem:presvalue} and Lemma~\ref{thm:pres-stride} are proven in the
appendix by induction over $e$. This subsequently allows us to prove
Theorem~\ref{thm:pres-norm}, again by induction over $e$.

@@

From Theorem~\ref{thm:pres-handle} and Theorem~\ref{thm:pres-norm} we directly
obtain that the driving semantics also preserves types.

@@

We define what we mean with progress in Theorem~\ref{thm:prog-norm}.
\begin{theorem}[Progress under handling]
  For all well typed expressions $e$ and states $s$,
  % For all expressions $e$ and states $s$
  % such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers s$,
  if $e,s \normalise e',s'$,
  then either $\Failing(e', s')$
  or there exist $e''$, $s''$, and $i$ such that $e',s'\handle{i} e'',s''$.
  \label{thm:prog-norm}
\end{theorem}

@@

We now have the ingredients to prove Theorem~\ref{thm:prog-norm}.

@@

  There does not exist an $i$ such that $e',s'\handle{i} e'',s''$. In this case, we
  know that $\Failing(e',s')$ must be true, by Theorem~\ref{thm:failing}.
\end{proof}

@@

In order to validate the function that calculates all possible inputs $\Inputs$,
we want to show that the set of possible inputs it produces is both sound and complete with respect to the handle semantics.
By sound we mean that all inputs in the set of possible inputs can actually be handled by the handle semantics,
and by complete we mean that the set of possible inputs contains all inputs that can be handled by the handle semantics.
Theorem~\ref{thm:safety-i} expresses exactly this property.

>>>>

\Cref{thm:pres-eval} is shown to be correct by induction over $e$. The full
proof can be found in the appendix.

@@

\Cref{lem:presvalue} and \cref{thm:pres-stride} are proven in the
appendix by induction over $e$. This subsequently allows us to prove
\Cref{thm:pres-norm}, again by induction over $e$.

@@

From \cref{thm:pres-handle} and \cref{thm:pres-norm} we directly
obtain that the driving semantics also preserves types.

@@

We define what we mean with progress in \cref{thm:prog-norm}.
\begin{theorem}[Progress under handling]
  For all well typed expressions $e$ and states $s$,
  % For all expressions $e$ and states $s$
  % such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers s$,
  if $e,s \normalise e',s'$,
  then either $\Failing(e', s')$
  or there exist $e''$, $s''$, and $i$ such that $e',s'\handle{i} e'',s''$.
  \label{thm:prog-norm}
\end{theorem}

@@

We now have the ingredients to prove \cref{thm:prog-norm}.

@@

  There does not exist an $i$ such that $e',s'\handle{i} e'',s''$. In this case, we
  know that $\Failing(e',s')$ must be true, by \cref{thm:failing}.
\end{proof}

@@

In order to validate the function that calculates all possible inputs $\Inputs$,
we want to show that the set of possible inputs it produces is both sound and complete with respect to the handle semantics.
By sound we mean that all inputs in the set of possible inputs can actually be handled by the handle semantics,
and by complete we mean that the set of possible inputs contains all inputs that can be handled by the handle semantics.
\Cref{thm:safety-i} expresses exactly this property.
